EvoSuite at the SBST 2017 Tool Competition

### 2017-02-18 papers/sbst17/paper_sbst17.tex
Some text describing setup

\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption{Classification of the \EVOSUITE unit test generation
  tool.}\label{tool-description}
\resizebox{1.0\columnwidth}{!}{  
\begin{tabular}{|l|p{5cm}|}
  \hline
  \multicolumn{2}{|l|}{Prerequisites} \\
  \hline
  Static or dynamic &  Dynamic testing at the Java class level\\
  Software Type &  Java classes\\
  Lifecycle phase&  Unit testing for Java programs\\
  Environment&  All Java development environments \\
  Knowledge required & JUnit unit testing for Java\\
  Experience required &  Basic unit testing knowledge\\
 \hline
  \multicolumn{2}{|l|}{Input and Output of the tool} \\
  \hline
 Input & Bytecode of the target class and dependencies \\
\hline
Output&  JUnit test cases (version 3 or 4)\\

@@

\EVOSUITE~\cite{FrA11c,GoA_TSE12} automatically generates test suites
for Java classes, targeting branch coverage and other coverage
criteria (e.g., mutation testing~\cite{emse14_mutation}). \EVOSUITE
works at the Java bytecode level, i.e., it does not require source
code. It is fully automated and requires no manually written test
drivers or parameterized unit tests.  For example, when \EVOSUITE is
used from its Eclipse and IntelliJ plugins, a user
just needs to select a class, and tests are generated with a mouse-click.

\EVOSUITE has been evaluated on millions of lines of Java
code~\cite{fraser2014large}, both open-source code and close-source
code provided by one of our industrial partners.  In the first two
editions of the unit testing tool competition, \EVOSUITE ranked
first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}, whereas it
ranked second in the third one.

\EVOSUITE uses an evolutionary approach to derive these test suites: A
genetic algorithm evolves candidate individuals (chromosomes) using
operators inspired by natural evolution (e.g., selection, crossover
and mutation), such that iteratively better solutions with respect to
the optimization target (e.g., branch coverage) are produced.  For
details on this test generation approach we refer to~\cite{GoA_TSE12}.
%To improve performance further, we are investigating several
%extensions to \EVOSUITE. 
%For example, \EVOSUITE can employ dynamic
%symbolic execution~\cite{evoISSRE113} 
%and memetic algorithms~\cite{fraser2014memetic}
%to handle the cases in which our genetic algorithm may struggle.

As the generated unit tests are meant for human
consumption~\cite{fraser2013does}, \EVOSUITE applies various
post-processing steps to improve readability (e.g., minimising) and
adds test assertions that capture the current behavior of the tested
classes. To select the most effective assertions, \EVOSUITE uses
mutation analysis~\cite{10.1109/TSE.2011.93}.  \EVOSUITE can also be
used to automatically find faults such as undeclared thrown exceptions
and broken code contracts~\cite{emse13_oracle}.  For more details on
the tool and its abilities we refer to~\cite{FrA11c,FrA13a}.

@@

\EVOSUITE can be configured to target different coverage criteria. The
fitness function to drive the genetic algorithm was based on a
combination of several criteria~\cite{rojas2015combining} (e.g., line
coverage, branch coverage, branch coverage by direct method
invocation, weak mutation testing, output coverage, exception
coverage). \EVOSUITE now by default uses an archive of
solutions~\cite{emse_archive}, which means that throughout the search,
whenever a new coverage goal is satisfied, the corresponding test is
stored in the archive, and this goal is no longer targeted by the
fitness function. We enabled the post-processing step of test
minimization, but to reduce the time spent we included all assertions
rather than filtering them with mutation
analysis~\cite{10.1109/TSE.2011.93}. The use of all assertions has
effects on readability and the chances of obtaining flaky
tests. However, as readability is not measured by the SBST contest
metric, and many of the improvements to \EVOSUITE since the last
competition target flaky tests, we deemed this not a problem.

In contrast to previous instances of the competition, the test
generation tools this time received a time budget as input, and then
had to generate tests within that time. \EVOSUITE uses a combination
of different timeouts for its individual phases (e.g., initialization,
search, minimization, assertion generation, compilation check, removal
of flaky tests), which created the challenge of distributing the
overall budget onto these phases. We used a simple approach where 50\%
of the time was allocated to the search, whereas the other half of the
time was distributed equally to the remaining phases. If any of the
phases used more time than allocated, which can for example happen if
test executions take long or lead to timeouts, then phases for which
there is no time left are skipped. For example, if there is no time
left for minimization, then the raw test suite as generated by the
search is returned.

>>>>

\begin{table}[!h]
\renewcommand{\arraystretch}{1.3}
\caption{Classification of the \EVOSUITE unit test generation
  tool.}\label{tool-description}
\resizebox{1.0\columnwidth}{!}{  
\begin{tabular}{|l|p{5cm}|}
  \hline
  \multicolumn{2}{|l|}{Prerequisites} \\
  \hline
  Static or dynamic &  Dynamic testing at the Java class level\\
  Software Type &  Java classes\\
  Lifecycle phase&  Unit testing for Java programs\\
  Environment&  All Java development environments \\
  Knowledge required & JUnit unit testing for Java\\
  Experience required &  Basic unit testing knowledge\\
 \hline
  \multicolumn{2}{|l|}{Input and Output of the tool} \\
  \hline
 Input & Bytecode of the target class and dependencies \\
\hline
Output&  JUnit 4 test cases\\

@@

\EVOSUITE~\cite{FrA11c} is a search-based tool~\cite{GoA_TSE12} that
uses a genetic algorithm to automatically generate test suites for
Java classes. Given the name of a target class and the full Java
classpath (i.e., where to find the compiled bytecode of the class
under test and all its dependencies), \EVOSUITE automatically produces
a set of JUnit test cases that maximise the achieved code
coverage. \EVOSUITE can be used on the command line, or through
plugins for popular development tools such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

The underlying genetic algorithm uses test suites as representation
(chromosomes). Each test suite consists of a variable number of test
cases, each of which is represented as a variable length sequence of
Java statements (e.g., calls on the class under test). A population of
randomly generated individuals is evolved using suitable search
operators (e.g., selection, crossover and mutation), such that
iteratively better solutions with respect to the optimisation target
are produced. The optimisation target is to maximise code coverage. To
achieve this, the fitness function uses standard heuristics such as
the branch distance; see~\cite{GoA_TSE12} for more details. \EVOSUITE
can be configured to optimise for multiple coverage criteria at the
same time, and the default configuration combines branch coverage with
mutation testing~\cite{emse14_mutation} and other basic
criteria~\cite{rojas2015combining}. Once the search is completed,
\EVOSUITE applies various optimisations to improve the readability of
the generated tests. For example, tests are minimised, and a
minimised set of effective test assertions is selected using mutation
analysis~\cite{10.1109/TSE.2011.93}. For more details on the tool and
its abilities we refer to~\cite{FrA11c,FrA13a}.

The effectiveness of \EVOSUITE has been evaluated on open source as
well as industrial software in terms of code
coverage~\cite{fraser2014large,emse_archive}, fault finding
effectiveness~\cite{shamshiri2015automatically,moein2017}, and effects
on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study}.

In the first two and the fourth editions of the unit testing tool
competition, \EVOSUITE ranked
first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013,evosuiteAtSbst2016},
whereas it ranked second in the third one.

%To improve performance further, we are investigating several
%extensions to \EVOSUITE. 
%For example, \EVOSUITE can employ dynamic
%symbolic execution~\cite{evoISSRE113} 
%and memetic algorithms~\cite{fraser2014memetic}
%to handle the cases in which our genetic algorithm may struggle.

@@

The configuration of \EVOSUITE for the competition is largely based on
its default values, since these have been tuned
extensively~\cite{arcuri2013parameter}. We used the default set of
coverage criteria~\cite{rojas2015combining} (e.g., line coverage,
branch coverage, branch coverage by direct method invocation, weak
mutation testing, output coverage, exception coverage). The use of an
archive of solutions~\cite{emse_archive}, which iteratively removes
covered goals from the fitness function and stores the corresponding
test cases is now enabled by default in \EVOSUITE.

A new feature in \EVOSUITE is the use of Mockito mock
classes~\cite{ICST_Mocking17}. After a certain percentage of the
search budget has passed, \EVOSUITE starts considering the use of mock
objects instead of real classes. Only branches that cannot be covered
without mocks will result in tests with mock objects in the end. We
further added frequency based weighting to constants for
seeding~\cite{sakti2015instance}, and included extensions to support
Java Enterprise Edition features~\cite{arcuri2016java}. Besides these
changes, several bug fixes were applied since the last instance of the
competition, in particular in relation to non-determinism and flaky
tests~\cite{ase14_environment}.

Like in previous instances of the competition, we enabled the
post-processing step of test minimisation (but not for efficiency
reasons, but because minimised tests are less likely to break). To
reduce the overall time of test generation we included all assertions
rather than filtering them with mutation
analysis~\cite{10.1109/TSE.2011.93}, which is a computationally
expensive process. The use of all assertions has a negative impact on
readability, but this is not evaluated as part of the SBST contest.

Like in the 2016 competition, tools were called with different time
budgets. We used the same strategy as for the previous
competition~\cite{evosuiteAtSbst2016} to distribute the overall time
budget onto the different phases of \EVOSUITE (e.g., initialization,
search, minimization, assertion generation, compilation check, removal
of flaky tests). That is, 50\% of the time was allocated to the
search, and the rest was distributed equally to the remaining
phases.
